Adaptive broadcast tree for multicores

### 2013-06-04 graphs/visu_sbrinz_binarytree.tex
Added forgotten file

\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
\node at (0mm,240mm) {core 16};
\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
\node at (0mm,255mm) {core 17};
\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
\node at (0mm,270mm) {core 18};
\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
\node at (0mm,285mm) {core 19};
\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
\node at (0mm,300mm) {core 20};
\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
\node at (0mm,315mm) {core 21};
\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
\node at (0mm,330mm) {core 22};
\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
\node at (0mm,345mm) {core 23};
\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
\node at (0mm,360mm) {core 24};
\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
\node at (0mm,375mm) {core 25};
\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
\node at (0mm,390mm) {core 26};
\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
\node at (0mm,405mm) {core 27};
\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
\node at (0mm,420mm) {core 28};
\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
\node at (0mm,435mm) {core 29};
\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
\node at (0mm,450mm) {core 30};
\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
\node at (0mm,465mm) {core 31};
\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
\node at (0mm,480mm) {Machine: gruyere, topology: binarytree};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (92mm,45mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (102mm,45mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (111mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (121mm,60mm) {};

@@

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (122mm,105mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (132mm,105mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (142mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (122mm,120mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (132mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (142mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (131mm,135mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (141mm,135mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (151mm,135mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_14_30) at (151mm,210mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_14_29) at (161mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (141mm,150mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (151mm,150mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (161mm,150mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_13_28) at (161mm,195mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_13_27) at (171mm,195mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (161mm,165mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_11_24) at (171mm,165mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_26) at (161mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_25) at (171mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (162mm,225mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_15_31) at (172mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_14_30) at (171mm,450mm) {};
\draw[->,very thick,color=red] (s_14_30.center) -- (r_14_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
\draw[->,very thick,color=red] (s_7_16.center) -- (r_7_16.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_18) at (172mm,270mm) {};
\draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (181mm,285mm) {};
\draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (181mm,300mm) {};
\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_28) at (181mm,420mm) {};
\draw[->,very thick,color=red] (s_13_28.center) -- (r_13_28.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (181mm,330mm) {};
\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_26) at (181mm,390mm) {};
\draw[->,very thick,color=red] (s_12_26.center) -- (r_12_26.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_14_29) at (181mm,435mm) {};
\draw[->,very thick,color=red] (s_14_29.center) -- (r_14_29.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (182mm,255mm) {};
\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_27) at (191mm,405mm) {};
\draw[->,very thick,color=red] (s_13_27.center) -- (r_13_27.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_25) at (191mm,375mm) {};
\draw[->,very thick,color=red] (s_12_25.center) -- (r_12_25.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_11_24) at (191mm,360mm) {};
\draw[->,very thick,color=red] (s_11_24.center) -- (r_11_24.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (191mm,345mm) {};
\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (191mm,315mm) {};
\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_15_31) at (192mm,465mm) {};
\draw[->,very thick,color=red] (s_15_31.center) -- (r_15_31.center);

>>>>

\node at (0mm,240mm) {Machine: sbrinz, topology: binarytree};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (92mm,45mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (102mm,45mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (111mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (121mm,60mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (112mm,105mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (122mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (131mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (132mm,120mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (141mm,135mm) {};

@@

@@

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (152mm,225mm) {};

@@

### 2013-06-04 graphs/visu_sbrinz_cluster.tex
Added forgotten file

\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
\node at (0mm,240mm) {core 16};
\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
\node at (0mm,255mm) {core 17};
\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
\node at (0mm,270mm) {core 18};
\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
\node at (0mm,285mm) {core 19};
\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
\node at (0mm,300mm) {core 20};
\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
\node at (0mm,315mm) {core 21};
\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
\node at (0mm,330mm) {core 22};
\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
\node at (0mm,345mm) {core 23};
\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
\node at (0mm,360mm) {core 24};
\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
\node at (0mm,375mm) {core 25};
\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
\node at (0mm,390mm) {core 26};
\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
\node at (0mm,405mm) {core 27};
\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
\node at (0mm,420mm) {core 28};
\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
\node at (0mm,435mm) {core 29};
\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
\node at (0mm,450mm) {core 30};
\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
\node at (0mm,465mm) {core 31};
\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
\node at (0mm,480mm) {Machine: gruyere, topology: cluster};

@@

@@

\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_16) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (110mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (130mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (90mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (100mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (110mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (120mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (130mm,120mm) {};

@@

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (120mm,360mm) {};
\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (130mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (140mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (150mm,360mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (120mm,180mm) {};
\draw[->,very thick,color=red] (s_4_12.center) -- (r_4_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (130mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (140mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (160mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (120mm,300mm) {};
\draw[->,very thick,color=red] (s_8_20.center) -- (r_8_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (130mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (140mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (150mm,300mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (121mm,165mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (121mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_16) at (130mm,240mm) {};
\draw[->,very thick,color=red] (s_4_16.center) -- (r_4_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (140mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (150mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (160mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (131mm,150mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (131mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (141mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (141mm,405mm) {};
\draw[->] (s_24_27.center) -- (r_24_27.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (141mm,135mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (141mm,345mm) {};
\draw[->] (s_20_23.center) -- (r_20_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (150mm,420mm) {};
\draw[->,very thick,color=red] (s_12_28.center) -- (r_12_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (160mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (170mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (180mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (151mm,330mm) {};
\draw[->] (s_20_22.center) -- (r_20_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (151mm,225mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (151mm,285mm) {};
\draw[->] (s_16_19.center) -- (r_16_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (151mm,390mm) {};
\draw[->] (s_24_26.center) -- (r_24_26.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (161mm,315mm) {};
\draw[->] (s_20_21.center) -- (r_20_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (161mm,270mm) {};
\draw[->] (s_16_18.center) -- (r_16_18.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (161mm,375mm) {};
\draw[->] (s_24_25.center) -- (r_24_25.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (171mm,255mm) {};
\draw[->] (s_16_17.center) -- (r_16_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (171mm,465mm) {};
\draw[->] (s_28_31.center) -- (r_28_31.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (171mm,195mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (181mm,450mm) {};
\draw[->] (s_28_30.center) -- (r_28_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (191mm,435mm) {};
\draw[->] (s_28_29.center) -- (r_28_29.center);

>>>>

\node at (0mm,240mm) {Machine: sbrinz, topology: cluster};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (90mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (100mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (110mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (120mm,120mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (110mm,60mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (101mm,105mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (110mm,180mm) {};
\draw[->,very thick,color=red] (s_8_12.center) -- (r_8_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (120mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (130mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (111mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (111mm,165mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (121mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (121mm,150mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (131mm,135mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (131mm,225mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (141mm,210mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};

@@

### 2013-06-04 graphs/visu_sbrinz_mst.tex
Added forgotten file

\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
\node at (0mm,240mm) {core 16};
\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
\node at (0mm,255mm) {core 17};
\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
\node at (0mm,270mm) {core 18};
\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
\node at (0mm,285mm) {core 19};
\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
\node at (0mm,300mm) {core 20};
\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
\node at (0mm,315mm) {core 21};
\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
\node at (0mm,330mm) {core 22};
\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
\node at (0mm,345mm) {core 23};
\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
\node at (0mm,360mm) {core 24};
\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
\node at (0mm,375mm) {core 25};
\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
\node at (0mm,390mm) {core 26};
\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
\node at (0mm,405mm) {core 27};
\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
\node at (0mm,420mm) {core 28};
\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
\node at (0mm,435mm) {core 29};
\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
\node at (0mm,450mm) {core 30};
\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
\node at (0mm,465mm) {core 31};
\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
\node at (0mm,480mm) {Machine: gruyere, topology: cluster};
\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (60mm,0mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_16) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (110mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (130mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (90mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (100mm,120mm) {};

@@

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (120mm,360mm) {};
\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (130mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (140mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (150mm,360mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (120mm,180mm) {};
\draw[->,very thick,color=red] (s_4_12.center) -- (r_4_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (130mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (140mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (160mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (120mm,300mm) {};
\draw[->,very thick,color=red] (s_8_20.center) -- (r_8_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (130mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (140mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (150mm,300mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (121mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_16) at (130mm,240mm) {};
\draw[->,very thick,color=red] (s_4_16.center) -- (r_4_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (140mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (150mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (160mm,240mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (131mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (141mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (141mm,405mm) {};
\draw[->] (s_24_27.center) -- (r_24_27.center); 

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (141mm,345mm) {};
\draw[->] (s_20_23.center) -- (r_20_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (150mm,420mm) {};
\draw[->,very thick,color=red] (s_12_28.center) -- (r_12_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (160mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (170mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (180mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (151mm,330mm) {};
\draw[->] (s_20_22.center) -- (r_20_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (151mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (151mm,285mm) {};
\draw[->] (s_16_19.center) -- (r_16_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (151mm,390mm) {};
\draw[->] (s_24_26.center) -- (r_24_26.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (161mm,315mm) {};
\draw[->] (s_20_21.center) -- (r_20_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (161mm,270mm) {};
\draw[->] (s_16_18.center) -- (r_16_18.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (161mm,375mm) {};
\draw[->] (s_24_25.center) -- (r_24_25.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (171mm,255mm) {};
\draw[->] (s_16_17.center) -- (r_16_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (171mm,465mm) {};
\draw[->] (s_28_31.center) -- (r_28_31.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (171mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (181mm,450mm) {};
\draw[->] (s_28_30.center) -- (r_28_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (191mm,435mm) {};
\draw[->] (s_28_29.center) -- (r_28_29.center);

>>>>

\node at (0mm,240mm) {Machine: sbrinz, topology: mst};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (60mm,0mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (110mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (80mm,180mm) {};
\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (90mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (100mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (110mm,180mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
\draw[->,very thick,color=red] (s_4_8.center) -- (r_4_8.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (101mm,225mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (101mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (111mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (111mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (121mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (121mm,75mm) {};

@@

@@

@@
